Metadata collation

### 2024-05-13 metadata/parametadata_control.Rmd
Organizing to factor by depth and startime

magick::image_read("http://scope.soest.hawaii.edu/data/scope2021/Paragon1CTDchlp.pdf", density = 300) %>%
  magick::image_trim() %>%
  magick::image_write("metadata/raw_data/chl_pdf_url.png", format = "png")
```

@@

```{r visualize}
my_casts <- c(4, 5, 9, 11, 13, 14, 16, 18, 25, 27, 31, 32, 34, 36, 39, 41)

@@

```{r write out}
write_csv(parametadata_all, file = "metadata/parametadata.csv")
```

>>>>

# magick::image_read("http://scope.soest.hawaii.edu/data/scope2021/Paragon1CTDchlp.pdf", density = 300) %>%
#   magick::image_trim() %>%
#   magick::image_write("metadata/raw_data/chl_pdf_url.png", format = "png")
```

@@

```{r visualize, eval=FALSE}
my_casts <- c(4, 5, 9, 11, 13, 14, 16, 18, 25, 27, 31, 32, 34, 36, 39, 41)

@@

```{r write out}
parametadata_all %>%
  mutate(depth=factor(depth, levels=c("Surf", "Deep"))) %>%
  mutate(startime=factor(startime, levels=c("Morn", "Eve"))) %>%
  arrange(polarity, amendment, depth, startime, timepoint_num, tripl) %>%
  write_csv(file = "metadata/parametadata.csv")
```
